### 2019-06-13 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
Quite a weird change of outline, but I like it!

As we said, a third possible approach is to select \emph{on the run} the best algorithm for a specific situation, for which the so called \emph{expert aggregation algorithms} framework can be useful.
%
To the best of our knowledge, aggregation algorithms, such as \ExpQ{} which dates back from 2002 \cite{Auer02},
have never been used in pratice for stochastic MAB problems.
% and we show that it appears empirically sub-optimal when applied to simple stochastic problems.

We present an improved variant of \ExpQ, called \Aggr.
For synthetic MAB problems, with Bernoulli or other distributions for $K$ arms, simulation results are presented to demonstrate its empirical efficiency.
We combine classical algorithms, such as Thompson sampling, Upper-Confidence Bounds algorithms (\UCB{} and variants), and Bayesian or Kullback-Leibler UCB.
%
Our algorithm offers good performance compared to state-of-the-art algorithms
(\ExpQ{}, \CORRAL{} or \LearnExp{}) \cite{Agarwal16,Singla17},
and appears as a robust approach to select on the run the best algorithm for any stochastic MAB problem, being more realistic to real-world radio settings than any tuning-based approach.

@@

% ----------------------------------------------------------------------
% \subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
\textbf{Notations:}\label{sub:25:aggregation}
%
We assume to have $N \geq 2$ MAB algorithms, $\Alg_1, \dots, \Alg_N$,
and let $\Alg_{\mathrm{aggr}}$ be an aggregation algorithm,
which runs the $N$ algorithms in parallel (with the same slotted time), and use them to choose its arms based on a voting from their $N$ decisions.
%
$\Alg_{\mathrm{aggr}}$ depends on a pool of algorithms and a set of parameters.
We would like that $\Alg_{\mathrm{aggr}}$
performs almost as well as the best of the $\Alg_a$, with a good choice of its parameters, independently of the MAB problem.
Ideally $\Alg_{\mathrm{aggr}}$ should perform similarly to the best of the $\Alg_a$.
%
To simplify the presentation, we only aggregate bandit algorithms that give deterministic recommendations:
one arm is chosen with probability $1$ and the others with probability $0$.
However, both \ExpQ{} and \Aggr{} can be adapted to aggregate randomized bandit algorithms, \ie, algorithms that output a probability distribution $\xi_t$ over the arms $[K]$ at each time step, and draw the next selected arm according to this distribution
(\eg, Thompson sampling).

@@

% ----------------------------------------------------------------------
\subsection{Our contribution: the \Aggr{} algorithm}\label{sub:25:Aggr}

\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			% \KwIn{Number of arms, $K \geq 2$}
			% \KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t}_j \eqdef \sum\limits_{a = 1}^{N} \pi^{t}_a \times \indic(\{A_a(t) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t) \sim p^{t}$\;
				% $\P(A(t)_{\mathrm{aggr}} = j) = p^{t}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t), r(t))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the reward, $\widehat{r}(t) = r(t) / p^{t}_{A(t)}$\;
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (reward $\ell_{A(t),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t r(t)) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
					}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t r(t) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} \eqdef \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

@@

The reward estimate is unbiased in the following sense. If one had access to the samples $Y_{k,t}$ for all arms $k$, the reward incurred by algorithm $a$ at time $t$ would be $r^a(t) = Y_{A_a(t),t}$.
But we are not in the full information setting (see \cite{CesaLugosi06}), but in the bandit setting, so only one of the samples $Y_{k,t}$ can be observed, $r(t)=Y_{A(t),t}$.
This quantity can only be observed for those algorithms $a$ for which $A_{a}^{t}=A(t)$.
However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $r^a(t)$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{r^a}(t) \eqdef \frac{Y_{A_a(t),t}}{p_{A_a(t)}^{t}} \indic(A_a(t) = A(t))
\end{equation}
then it satisfies $\E_{O_t}[\widehat{r^a}(t) | O_t] = Y_{A_a(t),t}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $O_t$.
%
Observe that $\widehat{r^a}(t) = 0$ for all algorithms $a$ such that $A_a(t) \neq A(t)$.

@@

% ----------------------------------------------------------------------
\textbf{Comparison with \ExpQ{}:}\label{sub:25:Exp4}
%
% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm dates from \cite{Auer02NonStochastic}, and for instance it is also well explained in Section~4.2 of \cite{Bubeck12}.
It is similar to \Aggr{}, presented in Algorithm~\ref{algo:25:Aggr},
but differs in the two following points.
%
The first difference is that $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t}$.
Then, \ExpQ{} gives back an observation (arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
The second difference is that after having computed the reward estimate $\widehat{r^a}(t)$, \ExpQ{} updates the estimated cumulative reward for each algorithm,
$\widetilde{R}_a(t) = \sum_{s=1}^{t} \widehat{r^a}(t) \times \indic(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead
\footnote{~It is the same for constant learning rates, and does not differ much for decreasing learning rates.}
of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(\eta_t \widetilde{R}_a(t))$.
%
We also note that \ExpQ{} uses \emph{losses} instead of rewards, with $\ell(t) = 1 - r(t)$, but this is only a change of vocabulary.

\textbf{How to choose the learning rates $(\eta_t)$:}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), the best choice is given by $\eta_t \eqdef \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic\footnote{~For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}.} to assume a fixed and known time horizon, so we prefer the alternative horizon-free choice%
\footnote{~It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.}
of learning rates,
$\eta_t \eqdef \log(N) / (t K)$ suggested by \cite{Bubeck12}.
We compare both approaches empirically, and the second one usually performs better.
We also stick to this choice of $(\eta_t)_{t \geq 1}$ for \Aggr.

% ----------------------------------------------------------------------
\subsection{Experiments on simulated MAB problems}\label{sub:25:numExp}

@@

\begin{figure}[b!]  % [htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}

@@

% ----------------------------------------------------------------------
\paragraph{No theoretical guarantees.}\label{sub:25:theory}

@@

% ----------------------------------------------------------------------
\paragraph{Conclusion about our \Aggr{} algorithm.}\label{sub:25:conclusion}

We presented the use of aggregation algorithms in the context of Opportunistic Spectrum Access for Cognitive Radio,
especially for the real-world setting of unknown problem instances,
when tuning parameters before-hand is no longer possible and an adaptive algorithm is preferable.
% - \ExpQ and \Aggr works fine
% Both algorithms \ExpQ{} and \Aggr{} have been detailed, and we explained why
Our proposed \Aggr{} was presented in details,
and we also highlighted its differences with \ExpQ.
% as well \color{red} as the intuition that it seems more suited for purely stochastic problems\color{black}.
%
% - \Aggr{} really help to select the best algorithm against a certain problem, on the fly without any prior knowledge of the problem neither any prior knowledge on which algorithms is the best
We presented experiments on simple MAB problems coming from previous work on bandits for OSA \cite{Jouini10},
and the simulations results showed that \Aggr{} is able to identify on the fly the best algorithm to trust for a specific problem, as expected.
Experiments on problems mixing different families of distributions were also presented, with similar conclusions in favor of \Aggr.
% It is not presented in this section, but our proposed algorithm also works well in dynamic scenarios, in which the distribution of the arms can change abruptly at some time,
% and appears to be more robust than simple non-aggregated algorithms.

\ExpQ{} has theoretical guarantees in terms of adversarial regret, and even if the same result could hold for \Aggr, results in terms of classical regret are yet to be proven.
Empirically, \Aggr{} showed to always have a logarithmic
regret $R_T$ if it aggregates algorithms with logarithmic regrets (like UCB, \klUCB, Thompson sampling, BayesUCB etc).
It usually succeeds to be close to the best of the aggregated algorithms, both in term of regret and best arm pull frequency.
As expected, the \Aggr{} is never able to outperform any of the aggregated algorithms, but this was an over-optimistic goal.
%
What matters the most is that, empirically, \Aggr{} is able to quickly discover \emph{on the fly} the best algorithms to trust, and then performs almost as well as if it was following it from the beginning.
%
%
Our \Aggr{} algorithm could probably be rewritten as an Online Mirror Descent (for more details, see for instance \cite{Hazan2016introduction,Zimmert2018}), as it is the case for both \ExpQ{} and \CORRAL.
But this direction does not appear very useful, as in the case of \CORRAL{}  the analysis cannot bring a logarithmic regret bound, even by aggregating asymptotically optimal algorithms.
% We will continue investigating regret bounds for \Aggr,
% and other directions include possible applications to the non-stochastic case (\eg, rested or restless Markovian problems, like it was very recently studied in \cite{Luo18}).

\paragraph{Reproducility of the experiments.}
%
Experiments presented in this Section are based on our library SMPyBandits,
and the page \href{https://SMPyBandits.GitHub.io/Aggregation.html}{\texttt{SMPyBandits.GitHub.io/Aggregation.html}} gives instructions to reproduce them.

>>>>

As we said, a third possible approach is to select \emph{on the run} the best algorithm for a specific situation, for which the so called \emph{expert aggregation algorithms} framework can be useful.
%
To the best of our knowledge, aggregation algorithms, such as \ExpQ{} which dates back from 2002 \cite{Auer02},
have never been used in practice for stochastic MAB problems.
% and we show that it appears empirically sub-optimal when applied to simple stochastic problems.

We present an improved variant of \ExpQ, called \Aggr.
For synthetic MAB problems, with Bernoulli or other distributions for $K$ arms, simulation results are presented to demonstrate its empirical efficiency.
We combine classical algorithms, such as Thompson sampling, Upper-Confidence Bounds algorithms (\UCB{} and variants), and Bayesian or \klUCB.
%
Our algorithm offers good performance compared to state-of-the-art algorithms
(\ExpQ{}, \CORRAL{} or \LearnExp{}) \cite{Agarwal16,Singla17},
and appears as a robust approach to select on the run the best algorithm for any stochastic MAB problem, being more realistic to real-world radio settings than any tuning-based approach.

@@

% ----------------------------------------------------------------------
\subsection{Aggregating bandit algorithms}\label{sub:25:aggregation}
% \paragraph{Notations:}\label{sub:25:aggregation}
%
We assume to have $N \geq 2$ MAB algorithms, $\Alg_1, \dots, \Alg_N$,
and let $\Alg_{\mathrm{aggr}}$ be an aggregation algorithm,
which runs the $N$ algorithms in parallel (with the same slotted time), and use them to choose its arms based on a voting from their $N$ decisions.
%
$\Alg_{\mathrm{aggr}}$ depends on a pool of algorithms and a set of parameters.
We would like that $\Alg_{\mathrm{aggr}}$
performs almost as well as the best of the $\Alg_a$, with a good choice of its parameters, independently of the MAB problem.
Ideally $\Alg_{\mathrm{aggr}}$ should perform similarly to the best of the $\Alg_a$.
%
To simplify the presentation, we only aggregate bandit algorithms that give deterministic recommendations:
one arm is chosen with probability $1$ and the others with probability $0$.
However, both \ExpQ{} and \Aggr{} can be adapted to aggregate randomized bandit algorithms, \ie, algorithms that output a probability distribution $\xi_t$ over the arms $[K]$ at each time step, and draw the next selected arm according to this distribution
(\eg, Thompson sampling).

@@

% ----------------------------------------------------------------------
\section{Our contribution: the \Aggr{} algorithm}\label{sub:25:Aggr}

@@

% \begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			% \KwIn{Number of arms, $K \geq 2$}
			% \KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$, \eg, $\eta_t=\frac{\log(N)}{t K}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t}_j \eqdef \sum\limits_{a = 1}^{N} \pi^{t}_a \times \indic(\{A_a(t) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t) \sim p^{t}$\;
				% $\P(A(t)_{\mathrm{aggr}} = j) = p^{t}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t), r(t))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the reward, $\widehat{r}(t) = r(t) / p^{t}_{A(t)}$\;
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (reward $\ell_{A(t),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t) = A(t)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t r(t)) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
					}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t r(t) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} \eqdef \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
% \end{small}

\paragraph{Unbiased estimate of the rewards.}
%
The reward estimate is unbiased in the following sense. If one had access to the samples $Y_{k,t}$ for all arms $k$, the reward incurred by algorithm $a$ at time $t$ would be $r^a(t) = Y_{A_a(t),t}$.
But we are not in the full information setting (see \cite{CesaLugosi06}), but in the bandit setting, so only one of the samples $Y_{k,t}$ can be observed, $r(t)=Y_{A(t),t}$.
This quantity can only be observed for those algorithms $a$ for which $A_{a}^{t}=A(t)$.
However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $r^a(t)$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{r^a}(t) \eqdef \frac{Y_{A_a(t),t}}{p_{A_a(t)}^{t}} \indic(A_a(t) = A(t))
\end{equation}
then it satisfies $\E_{O_t}[\widehat{r^a}(t) | O_t] = Y_{A_a(t),t}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $O_t$.
%
Observe that $\widehat{r^a}(t) = 0$ for all algorithms $a$ such that $A_a(t) \neq A(t)$.

@@

% ----------------------------------------------------------------------
\paragraph{Comparison with \ExpQ{}:}\label{sub:25:Exp4}
%
% - explain, but don't give pseudo-code ?
The \ExpQ{} algorithm dates from \cite{Auer02NonStochastic}, and for instance it is also well explained in Section~4.2 of \cite{Bubeck12}.
It is similar to \Aggr{}, presented in Algorithm~\ref{algo:25:Aggr},
but differs in the two following points.
%
The first difference is that $a\sim\pi^t$ is sampled first and the arm chosen by $\Alg_a$ is trusted, whereas \Aggr{}
needs to listen to the $N$ decisions to perform the updates on $\pi^{t}$.
Then, \ExpQ{} gives back an observation (arm, reward) only to the last trusted algorithm
whereas \Aggr{} gives it to all algorithms.
%
The second difference is that after having computed the reward estimate $\widehat{r^a}(t)$, \ExpQ{} updates the estimated cumulative reward for each algorithm,
$\widetilde{R}_a(t) = \sum_{s=1}^{t} \widehat{r^a}(t) \times \indic(A^{s}_{a} = A^{s}_{\mathrm{aggr}})$.
%
Instead
\footnote{~It is the same for constant learning rates, and does not differ much for decreasing learning rates.}
of updating $\pi^{t}$ multiplicatively as we do for our proposal, \ExpQ{} recomputes it, proportionally to
$\exp(\eta_t \widetilde{R}_a(t))$.
%
We also note that \ExpQ{} uses \emph{losses} instead of rewards, with $\ell(t) = 1 - r(t)$, but this is only a change of vocabulary.

\paragraph{How to choose the learning rates $(\eta_t)$:}
%
The sequence of non-negative learning rates $(\eta_t)_{t \geq 1}$ used by \ExpQ{} can be arbitrary.
It can be constant but should be non-increasing \cite[Theorem 4.2]{Bubeck12}.
% helps to choose a good sequence.
If the horizon $T$ is known (and fixed), the best choice is given by $\eta_t \eqdef \eta = 2 \log(N) / (T K)$.
However, for real-world communication problems, it can be considered unrealistic\footnote{~For more discussion on this hypothesis, we refer to Section~1 of our article \cite{Besson2018DoublingTricks}.} to assume a fixed and known time horizon, so we prefer the alternative horizon-free choice%
\footnote{~It is non-increasing, and is obtained by minimizing the upper-bound on the regret derived in \cite[pp48]{Bubeck12}.}
of learning rates,
$\eta_t \eqdef \log(N) / (t K)$ suggested by \cite{Bubeck12}.
We compare both approaches empirically, and the second one usually performs better.
We also stick to this choice of $(\eta_t)_{t \geq 1}$ for \Aggr.

% ----------------------------------------------------------------------
\section{Experiments on simulated MAB problems}\label{sub:25:numExp}

@@

\begin{figure}[b!]  % [htbp]
	\centering
	\includegraphics[width=1.10\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}

@@

% ----------------------------------------------------------------------
\subsection{No theoretical guarantees.}\label{sub:25:theory}

@@

% % ----------------------------------------------------------------------
% \paragraph{Conclusion about our \Aggr{} algorithm.}\label{sub:25:conclusion}

% We presented the use of aggregation algorithms in the context of Opportunistic Spectrum Access for Cognitive Radio,
% especially for the real-world setting of unknown problem instances,
% when tuning parameters before-hand is no longer possible and an adaptive algorithm is preferable.
% % - \ExpQ and \Aggr works fine
% % Both algorithms \ExpQ{} and \Aggr{} have been detailed, and we explained why
% Our proposed \Aggr{} was presented in details,
% and we also highlighted its differences with \ExpQ.
% % as well \color{red} as the intuition that it seems more suited for purely stochastic problems\color{black}.
% %
% % - \Aggr{} really help to select the best algorithm against a certain problem, on the fly without any prior knowledge of the problem neither any prior knowledge on which algorithms is the best
% We presented experiments on simple MAB problems coming from previous work on bandits for OSA \cite{Jouini10},
% and the simulations results showed that \Aggr{} is able to identify on the fly the best algorithm to trust for a specific problem, as expected.
% Experiments on problems mixing different families of distributions were also presented, with similar conclusions in favor of \Aggr.
% % It is not presented in this section, but our proposed algorithm also works well in dynamic scenarios, in which the distribution of the arms can change abruptly at some time,
% % and appears to be more robust than simple non-aggregated algorithms.

% \ExpQ{} has theoretical guarantees in terms of adversarial regret, and even if the same result could hold for \Aggr, results in terms of classical regret are yet to be proven.
% Empirically, \Aggr{} showed to always have a logarithmic
% regret $R_T$ if it aggregates algorithms with logarithmic regrets (like UCB, \klUCB, Thompson sampling, BayesUCB etc).
% It usually succeeds to be close to the best of the aggregated algorithms, both in term of regret and best arm pull frequency.
% As expected, the \Aggr{} is never able to outperform any of the aggregated algorithms, but this was an over-optimistic goal.
% %
% What matters the most is that, empirically, \Aggr{} is able to quickly discover \emph{on the fly} the best algorithms to trust, and then performs almost as well as if it was following it from the beginning.
% %
% %
% Our \Aggr{} algorithm could probably be rewritten as an Online Mirror Descent (for more details, see for instance \cite{Hazan2016introduction,Zimmert2018}), as it is the case for both \ExpQ{} and \CORRAL.
% But this direction does not appear very useful, as in the case of \CORRAL{}  the analysis cannot bring a logarithmic regret bound, even by aggregating asymptotically optimal algorithms.
% % We will continue investigating regret bounds for \Aggr,
% % and other directions include possible applications to the non-stochastic case (\eg, rested or restless Markovian problems, like it was very recently studied in \cite{Luo18}).

% \paragraph{Reproducility of the experiments.}
% %
% Experiments presented in this Section are based on our library SMPyBandits,
% and the page \href{https://SMPyBandits.GitHub.io/Aggregation.html}{\texttt{SMPyBandits.GitHub.io/Aggregation.html}} gives instructions to reproduce them.
